\mutagen: Coverage-Guided, Property-Based Testing using Exhaustive Structure-Preserving Mutations

### 2022-03-08 papers/fse22/main.tex
Added threats to validity

The second heuristic adjusts the number of test cases generated by random
mutations. 
%
% number of times our tool samples random
% mutants, i.e., those corresponding to large enumeration types as described
% above.
%
For this, we keep track of how often we generate interesting test cases.
%
If this frequency stalls, \mutagen resets the testing loop and increases the
effort put into sampling random mutations.
%
This automatically finds a suitable value for this parameter on the fly.

@@

%% Pellentesque dapibus suscipit ligula. Donec posuere augue in quam. Etiam vel
%% tortor sodales tellus ultricies commodo. Suspendisse potenti. Aenean in sem ac
%% leo mollis blandit. Donec neque quam, dignissim in, mollis nec, sagittis eu,
%% wisi. Phasellus lacus. Etiam laoreet quam sed arcu. Phasellus at dui in ligula
%% mollis ultricies.

>>>>

The second heuristic adjusts the number of test cases generated from random
mutations  
%
% number of times our tool samples random
% mutants, i.e., those corresponding to large enumeration types as described
% above.
%
by monitoring how often we generate interesting test cases.
%
If this frequency stalls, \mutagen resets the testing loop and increases the
effort put into sampling random mutations.
%
This automatically finds a suitable value for this parameter on the fly.

@@

%% Pellentesque dapibus suscipit ligula. Donec posuere augue in quam. Etiam vel
%% tortor sodales tellus ultricies commodo. Suspendisse potenti. Aenean in sem ac
%% leo mollis blandit. Donec neque quam, dignissim in, mollis nec, sagittis eu,
%% wisi. Phasellus lacus. Etiam laoreet quam sed arcu. Phasellus at dui in ligula
%% mollis ultricies.
% ----------------------------------------

\section{Threats to Validity}
\label{sec:threats}

% Limited evaluation
Our experiments cover generating test cases in two substantially different
scenarios (valid IFC machine states and WebAssembly programs). 
%
Nonetheless, we cannot generalize that \mutagen will be effective at finding
bugs in other systems or testing properties. 
%
However, our tool can automatically synthesize all the boilerplate code required
to operate, becoming a drop-in replacement of \quickcheck (the most ubiquitous
RPBT tool in Haskell). 
%     
This makes it an appealing alternative whenever \quickcheck is unable to
penetrate some sparse precondition and simply gives up.

% Coq -> Haskell translation
As mentioned in \S \ref{sec:casestudies}, our evaluation required us to
translate the IFC state machine used by \citeauthor{lampropoulos2019coverage}
from Coq to Haskell. 
%
Although this translation could be done quite mechanically (this process was
partially aided by Coq's code extraction mechanism), we cannot guarantee that
our Haskell version of the code behaves exactly as the original one. 
%
% In addition, one should also consider some  
% that the specific performance the
% runtime systems of these two programming languages can affect, the
% draw strong conclusions based only on time-to-failure.
